Replication on multicore considering hierarchy and characteristics of the network

### 2013-03-14 paper.tex
Updated numbers. Added graph showing broadcast tree on gruyere

% tikz stuff
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{shapes,positioning,calc}

@@

on revision 1190:a787513fd28c, experiments for sequential and batch
broadcast working on nos5 and appenzeller

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    broadcast algorithm & \multicolumn{2}{c}{nos5} & \multicolumn{2}{c}{gruyere} \\
      & cycles & error & cycles & error \\
    \midrule
    sequential &  4096.1 &  105.2 & 136751.9 &   3061.5 \\
    batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
    tree\footnote{This only works for the first 200 runs, after that,
      performance breaks down, don't know why, but the first 200 runs
      are quite stable}%
               &  \sout{1471.8} &  \sout{187.9} &          &          \\
    \bottomrule
  \end{tabular}
  \caption{Broadcast measurements}
  \label{tab:bc_measurements}
\end{table}

@@

>>>>

% tikz stuff
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes}

@@

\paragraph{Current numbers}

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    broadcast algorithm & \multicolumn{2}{c}{nos5} & \multicolumn{2}{c}{gruyere} \\
      & cycles & error & cycles & error \\
    \midrule
    sequential &  4096.1 &  105.2 & 136751.9 &   3061.5 \\
    batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
    \bottomrule
  \end{tabular}
  \caption{Broadcast measurements}
  \label{tab:bc_measurements}
\end{table}

\paragraph{Tree setup} \stefan{describe}

@@

\paragraph{Minimal cost of sending a tree-broadcast} %
Plot~\ref{pgfplot:201303141819} shows the minimal cost of flooding a
sub-tree. The group communication is based on a binary tree. Core 0 is
the root, cores 1 and 2 are its children etc.

The average cost is really high (so something is wrong with my
code). But the minimal numbers show what is possible. The numbers
achieved are easily explainable. The cost is increasing
logarithmic with the number of nodes reached by the broadcast (as
expected). Every level in the tree adds an additional 3500 cycles to
the tree. Node 0 takes significantly longer. I don't know yet why that
is.

\begin{figure}
  \caption{Plot}
  \label{pgfplot:201303141819}
  \begin{tikzpicture}
    \begin{axis}[
      xlabel=core id,
      ylabel={cost for subtree [cycles]}]
    \addplot[color=red,mark=x] coordinates {
      (0,9475.0)
      (1,7935.0)
      (2,7894.0)
      (3,5965.0)
      (4,5604.0)
      (5,5718.0)
      (6,5647.0)
      (7,4316.0)
      (8,2989.0)
      (9,3173.0)
      (10,3395.0)
      (11,3332.0)
      (12,3284.0)
      (13,3310.0)
      (14,3231.0)
      (15,2542.0)
      (16,586.0)
      (17,588.0)
      (18,576.0)
      (19,583.0)
      (20,536.0)
      (21,539.0)
      (22,533.0)
      (23,516.0)
      (24,546.0)
      (25,552.0)
      (26,541.0)
      (27,543.0)
      (28,537.0)
      (29,527.0)
      (30,533.0)
      (31,534.0)
    };
    \end{axis}
  \end{tikzpicture}

\end{figure}

\begin{figure}
  \input{qrm_tree_gruyere}
  \caption{Tree of cores for broadcast on gruyere}
\end{figure}
